VariantSpark: Population Scale Clustering of Genotype Information

### 2015-11-27 doc/publications/journal2014/paper.tex
typos and passive

\subsection*{Personal Genome Project Data}
We acquired genomic data from the Personal Genome Project (PGP) website (\url{https://my.pgp-hms.org/public_genetic_data}). We sorted the genotype data from 23andMe microarray platforms by genome 
build. Using custom shell scripts, we convert NCBI build 36 files to BED format, update to build 37 using UCSC liftOver (\url{https://genome.ucsc.edu/cgi-bin/hgLiftOver}) and 
then convert back to 23andMe format. We then convert the 23andMe files to VCF format using code obtained from the Broad Institute (\url{http://apol1.blogspot.com.au/2013/08/impute-apoe-and-apol1-with-23andme.html}). 
Where individuals had genotype data for both genome builds 36 and 37, only the latter was used. Finally, we combined the individual VCF files into one 
file for clustering, using VCFtools \cite{Danecek2011Variant}.

>>>>

\subsection*{Personal Genome Project Data}
We acquired genomic data from the Personal Genome Project (PGP) website (\url{https://my.pgp-hms.org/public_genetic_data}). We sort the genotype data from 23andMe microarray platforms by genome 
build. Using a custom shell script, we convert NCBI build 36 files to BED format, update to build 37 using UCSC liftOver (\url{https://genome.ucsc.edu/cgi-bin/hgLiftOver}) and 
then convert back to 23andMe format. We then convert the 23andMe files to VCF using code obtained from the Broad Institute (\url{http://apol1.blogspot.com.au/2013/08/impute-apoe-and-apol1-with-23andme.html}). 
Where individuals had genotype data for both genome builds 36 and 37, we only use the latter. Finally, we combined the individual VCF files into one 
file for clustering, using VCFtools \cite{Danecek2011Variant}.
